### 2013-03-31 doc/final_report/design.tex
Finished introduction to partridge views implementation

\subsection{ Target Platform}

@@

\subsection{ Data Storage }
It is expected that a given Partridge instance may grow in size to contain
thousands of individual papers that have been annotated and are available to
the web backend for inclusion into a user's search results. Reading in and
parsing each individual XML file stored in the system is not really feasible
when handling a HTTP request from the web frontend, this sort of process would
take a long time to execute. To provide fast search and retrieval of paper
data, a Relational Database Management server (RDBMS) was chosen for storage of
papers that have been preprocessed using the system described above. An
overview of the database schema is illustrated in Figure \ref{fig:e-r-diagram}.

@@

\subsection{ Web Frontend }

>>>>

\subsection{Target Platform}

@@

\subsection{ Data Storage }
\label{sec:db_layout}
It is expected that a given Partridge instance may grow in size to contain
thousands of individual papers that have been annotated and are available to
the web backend for inclusion into a user's search results. Reading in and
parsing each individual XML file stored in the system is not really feasible
when handling a HTTP request from the web frontend, this sort of process would
take a long time to execute. To provide fast search and retrieval of paper
data, a Relational Database Management server (RDBMS) was chosen for storage of
papers that have been preprocessed using the system described above. An
overview of the database schema is illustrated in Figure \ref{fig:e-r-diagram}.

@@

\subsection{ Web Frontend }
\label{sec:web_frontend}

### 2013-03-31 doc/final_report/implementation.tex
Finished introduction to partridge views implementation

The implementation of the server views was for the most part straight forward
with the exception of some of the responses to the interactive web elements in
the HTML markup. It was determined that the best way to communicate between
frontend and backend elements interactively was to encode responses as
JavaScript Object Notation JSON - a common notation used to describe arbitrary
data structures\cite{jsonRFC}. Despite its name, JSON encoders and decoders are available for
most common programming languages.  Flask even has an inbuilt method called
jsonify which can be used to automatically encode arbitrary Python objects as
JSON and send it back to the browser for parsing by the frontend scripts.

@@

@@

\subsection{Query Interface}

>>>>

The implementation of the server views was for the most part straight forward
with the exception of some of the responses to the interactive web elements in
the HTML markup. It was determined that the best way to communicate between
frontend and backend elements interactively was to encode responses as
JavaScript Object Notation JSON - a common notation used to describe arbitrary
data structures\cite{jsonRFC}. Despite its name, JSON encoders and decoders are
available for most common programming languages, not just JavaScript.  Flask
even has an inbuilt method called jsonify which can be used to automatically
encode arbitrary Python objects as JSON and send it back to the browser for
parsing by the frontend scripts\cite{flask2012}.

Some of the frontend scripts such as the Query Form rely upon the server to
return dynamically generated HTML markup containing data about the papers being
processed. In line with its model-view-controller architecture, flask provides
a templating module that can be used to populate pre-coded HTML templates with
data from the database on the fly. Templates for each of the views are stored
within the \emph{templates/} subdirectory within Partridge and are populated
using data retrieved from the relational database when a call to one of the
view functions is made\cite{flask2012}.

@@

Partridge makes extensive use of a relational database system for storage and
retrieval of paper data and metadata. It uses an SQL database server and
initially the schema listed in Section \ref{sec:db_layout}. Rather than using
raw SQL calls to communicate with the database, It was determined that the use
of an Object-Relation-Mapper (ORM) library such as SQLAlchemy could
significantly speed up development time. SQLAlchemy and ORM wrappers are used
to abstract database entities into language constructs.

SQLAlchemy enables the representation of papers, authors and other entities as
Python objects. These objects can also be extended and custom methods added to
them, enabling the creation of specific entity methods such as calculating
CoreSC makeup of papers and computing first, middle and last names from a
single input string of an author's full name.

@@

Partridge's web frontend required the least procedural programming and mainly
consists of HTML markup with some JavaScript. The layouts were based upon the
interface designs discussed in Section \ref{sec:web_frontend}. However, some
changes were made to the original designs during implementation to improve
usability functionality.

As discussed above, the HTML layouts were stored as templates in the
Partridge system and were evaluated and expanded using data from the SQL
server at runtime. Flask's database engine supports object oriented templates
that inherit properties from each other. This allowed the main page layout to
be designed once and reused for each specific view.

Bootstrap, a powerful design framework was used to help build the frontend
pages and forms. Bootstrap offers a set of standard CSS and JavaScript
utilities that assist the developer in designing page layouts and provide
commonly used boilerplate code and interface elements\cite{bootstrap2013}. This
allowed the page layouts and forms used in Partridge to be implemented a lot
quicker than if they had been implemented from scratch. jQuery, a library for
manipulating HTML page layouts using JavaScript and providing utility functions
for server communication, was also used to save time in writing the interactive
aspects of frontend code.

Whilst these libraries did not provide any assistance specific to the domains
of information retrieval or machine learning, they did help accelerate the
design of the frontend interfaces and provide cross-browser compatible HTML5
interfaces. Other javascript libraries providing multiple file upload
capability and browser history manipulation were incorporated into specific
user interface modules.

\subsection{Query Interface \& Results View}
